---
title: "HW 5"
Author: "Kelly Wang, kzw2102"
output: github_document
---

# Problem 1
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
* fill in missing numeric values with the mean of the non-missing values
* character variables, fill in missing values with "virginica"


* writing a function that takes a vector as an argument 
* replaces missing values using rules defined above 
* returns the returning vector
* applying this function to the columns of iris_meaning_missing using map statement 

```{r function}
replace_missing = function(x) {
  if (is.numeric(x)) {
    mean_x=mean(x)
    mean_x
    x=replace(x, is.na(x), mean_x)
  }else if (is.character(x)) {
    x=replace(x, is.na(x), "virginica")
  }
}

output = map(iris_with_missing, replace_missing)

output
```
## Problem 2
```{r}
readr::read_csv("./data/hw5_data.zip")
```

